---
title: "thesis_statistical_analysis"
author: "chiu meng-yu"
date: "2026-04-07"
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{threeparttable}
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

### 0. Setup

```{r}
library(tidyverse)
library(effectsize)
library(effsize)
library(broom)
library(knitr)
library(kableExtra)
library(irr)
library(boot)
library(caret)
```

### 1. Read data

```{r}
mentions_df <- read_csv(
  "results/mentions_with_content_words.csv",
  show_col_types = FALSE
)
```

### 2. Helper functions

```{r}
pick_first_existing <- function(data, candidates) {
  hit <- candidates[candidates %in% names(data)][1]
  if (is.na(hit)) return(NULL)
  hit
}

standardize_main_columns <- function(data) {
  gender_col <- pick_first_existing(data, c("gender_new", "gender_cascade", "cascade_gender"))
  state_col  <- pick_first_existing(data, c("state_new", "state_cascade", "cascade_state"))

  if (!is.null(gender_col) && gender_col != "gender_new") {
    data <- data %>% rename(gender_new = all_of(gender_col))
  }
  if (!is.null(state_col) && state_col != "state_new") {
    data <- data %>% rename(state_new = all_of(state_col))
  }

  data
}

# Cohen's d with pooled standard deviation (standard textbook formula).
cohens_d_pooled <- function(a, b) {
  a <- a[!is.na(a)]
  b <- b[!is.na(b)]

  n1 <- length(a)
  n2 <- length(b)
  s1 <- sd(a)
  s2 <- sd(b)

  pooled <- sqrt(((n1 - 1) * s1^2 + (n2 - 1) * s2^2) / (n1 + n2 - 2))
  if (is.na(pooled) || pooled == 0) return(0)

  (mean(a) - mean(b)) / pooled
}

# Bootstrap 95% CI for Cohen's d (percentile method, B=2000).
bootstrap_cohens_d_ci <- function(a, b, R = 2000, seed = 42) {
  set.seed(seed)
  a <- a[!is.na(a)]
  b <- b[!is.na(b)]

  point <- cohens_d_pooled(a, b)

  boots <- replicate(R, {
    a_star <- sample(a, length(a), replace = TRUE)
    b_star <- sample(b, length(b), replace = TRUE)
    cohens_d_pooled(a_star, b_star)
  })

  ci <- quantile(boots, c(0.025, 0.975), na.rm = TRUE)
  c(d = point, ci_low = unname(ci[1]), ci_high = unname(ci[2]))
}

p_to_stars <- function(p) {
  case_when(
    is.na(p) ~ "",
    p < 0.001 ~ "***",
    p < 0.01  ~ "**",
    p < 0.05  ~ "*",
    TRUE ~ "ns"
  )
}

# Macro-F1 computed from scratch (sklearn-style: per-class F1 then average).
macro_f1_sklearn_style <- function(truth, pred, labels) {
  truth <- as.character(truth)
  pred  <- as.character(pred)

  f1s <- sapply(labels, function(lbl) {
    tp <- sum(truth == lbl & pred == lbl, na.rm = TRUE)
    fp <- sum(truth != lbl & pred == lbl, na.rm = TRUE)
    fn <- sum(truth == lbl & pred != lbl, na.rm = TRUE)

    precision <- ifelse(tp + fp == 0, 0, tp / (tp + fp))
    recall    <- ifelse(tp + fn == 0, 0, tp / (tp + fn))

    if ((precision + recall) == 0) 0
    else 2 * precision * recall / (precision + recall)
  })

  mean(f1s)
}

bootstrap_macro_f1_exact <- function(data, truth_col, pred_col, labels,
                                     R = 1000, seed = 42) {
  set.seed(seed)

  truth <- data[[truth_col]]
  pred  <- data[[pred_col]]
  n <- length(truth)

  point <- macro_f1_sklearn_style(truth, pred, labels)

  boots <- replicate(R, {
    idx <- sample.int(n, size = n, replace = TRUE)
    macro_f1_sklearn_style(truth[idx], pred[idx], labels)
  })

  tibble(
    estimate = point,
    ci_low   = unname(quantile(boots, 0.025, na.rm = TRUE)),
    ci_high  = unname(quantile(boots, 0.975, na.rm = TRUE))
  )
}

pretty_p <- function(p) {
  case_when(
    is.na(p)      ~ "",
    p < 0.001     ~ "< .001",
    TRUE          ~ sprintf("%.3f", p)
  )
}
```

### 3. Standardize columns

```{r}
mentions_df <- standardize_main_columns(mentions_df)
```

### 4. Ghost gender distribution: Chi-square + Cramer's V

#### 4.1 Mention-level

```{r}
ghosts <- mentions_df %>%
  filter(state_new == "Supernatural",
         gender_new %in% c("Female", "Male"),
         !is.na(platform))

ct_mention <- table(ghosts$platform, ghosts$gender_new)

chisq_mention  <- chisq.test(ct_mention)
cramer_mention <- effectsize::cramers_v(ct_mention)
expected_min_mention <- min(chisq_mention$expected)

if (expected_min_mention < 5) {
  message("  ⚠ Mention-level: expected frequency < 5 (min = ",
          round(expected_min_mention, 2),
          ") — using Fisher's exact test as fallback.")
  fisher_mention <- fisher.test(ct_mention, simulate.p.value = TRUE, B = 10000)
  mention_result <- tibble(
    level     = "mention (Fisher)",
    chi2      = NA_real_,
    df        = NA_real_,
    p_value   = fisher_mention$p.value,
    cramers_v = cramer_mention$Cramers_v[1]
  )
} else {
  mention_result <- tibble(
    level     = "mention",
    chi2      = unname(chisq_mention$statistic),
    df        = unname(chisq_mention$parameter),
    p_value   = chisq_mention$p.value,
    cramers_v = cramer_mention$Cramers_v[1]
  )
}

mention_result
```

#### 4.2 Article-level robustness

```{r}
article_result <- NULL

if ("article_id" %in% names(ghosts)) {
  ghosts_article <- ghosts %>%
    distinct(article_id, gender_new, .keep_all = TRUE)

  ct_article <- table(ghosts_article$platform, ghosts_article$gender_new)

  # Check expected cell counts (cf. space_color notebook approach)
  chisq_article  <- chisq.test(ct_article)
  expected_min   <- min(chisq_article$expected)

  if (expected_min < 5) {
    message("  ⚠ Expected frequency < 5 in some cells (min = ",
            round(expected_min, 2),
            ") — using Fisher's exact test as fallback.")
    fisher_article <- fisher.test(ct_article, simulate.p.value = TRUE, B = 10000)
    article_result <- tibble(
      level     = "article (Fisher)",
      chi2      = NA_real_,
      df        = NA_real_,
      p_value   = fisher_article$p.value,
      cramers_v = effectsize::cramers_v(ct_article)$Cramers_v[1]
    )
  } else {
    cramer_article <- effectsize::cramers_v(ct_article)
    article_result <- tibble(
      level     = "article",
      chi2      = unname(chisq_article$statistic),
      df        = unname(chisq_article$parameter),
      p_value   = chisq_article$p.value,
      cramers_v = cramer_article$Cramers_v[1]
    )
  }

  ct_article
  article_result
}
```

#### 4.3 Latex

```{r results='asis'}
tab_43 <- bind_rows(mention_result, article_result) %>%
  mutate(across(where(is.numeric), ~round(., 4)))

cat(
  kbl(tab_43,
      format    = "latex",
      booktabs  = TRUE,
      caption   = "Ghost gender distribution across platforms (Fisher's exact test used when expected count $< 5$).",
      col.names = c("Level", "$\\chi^2$", "df", "$p$", "Cram\\'{e}r's $V$"),
      escape    = FALSE
  ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

### 5. LLR + raw p + BH-FDR + log odds ratio CI

```{r}
llr_ptt    <- read_csv("results/collocate_LLR_ptt.csv",    show_col_types = FALSE)
llr_reddit <- read_csv("results/collocate_LLR_reddit.csv",  show_col_types = FALSE)
llr_theqoo <- read_csv("results/collocate_LLR_theqoo.csv",  show_col_types = FALSE)
```

```{r}
llr_all <- bind_rows(
  llr_ptt    %>% mutate(platform = "PTT"),
  llr_reddit %>% mutate(platform = "Reddit"),
  llr_theqoo %>% mutate(platform = "TheQoo")
)

llr_all_fmt <- llr_all %>%
  mutate(word_sig = paste0(word, sig_fdr))

llr_top10 <- llr_all_fmt %>%
  filter(direction %in% c("Female", "Male")) %>%
  mutate(
    direction = recode(direction,
                       "Female" = "Female ghosts",
                       "Male"   = "Male ghosts")
  ) %>%
  group_by(platform, direction) %>%
  arrange(desc(abs(LLR)), .by_group = TRUE) %>%
  slice_head(n = 10) %>%
  summarise(
    `top-10 words` = paste(word_sig, collapse = ", "),
    .groups = "drop"
  ) %>%
  rename(`related gendered ghost` = direction) %>%
  arrange(platform, `related gendered ghost`)

llr_top10
```

```{r}
cat(
  llr_top10 %>%
    kbl(
      format    = "latex",
      booktabs  = TRUE,
      align     = c("l", "l", "l"),   
      col.names = c("Platform", "Related Gendered Ghost", "Top-10 Words"),
      caption   = "Top 10 gendered collocates by platform based on signed log-likelihood ratio (LLR)."
    ) %>%
    kable_styling(latex_options = c("hold_position")) %>%  
    column_spec(3, width = "10cm") %>%                      # 控制寬度
    footnote(
      general        = "*** $p < .001$, ** $p < .01$, * $p < .05$ (BH-FDR adjusted).",
      threeparttable = TRUE,
      escape         = FALSE
    )
)
```

### 6. Affect score comparison: Welch t-test + Cohen's d + Bonferroni

```{r}
affect_cols <- c("val_pos", "val_neg", "val_revenge")
platforms   <- c("ptt", "reddit", "theqoo")

ghosts_known <- mentions_df %>%
  filter(state_new == "Supernatural",
         gender_new %in% c("Female", "Male"))

run_affect_test <- function(data, platform_name, varname) {
  sub <- data %>% filter(platform == platform_name)

  fa <- sub %>% filter(gender_new == "Female") %>% pull(all_of(varname))
  ma <- sub %>% filter(gender_new == "Male")   %>% pull(all_of(varname))

  fa <- fa[!is.na(fa)]
  ma <- ma[!is.na(ma)]

  if (length(fa) < 5 || length(ma) < 5) return(NULL)

  tt    <- t.test(fa, ma, var.equal = FALSE)
  d_ci  <- bootstrap_cohens_d_ci(fa, ma)

  tibble(
    Platform    = platform_name,
    Metric      = varname,
    Female_n    = length(fa),
    Male_n      = length(ma),
    Female_mean = mean(fa),
    Male_mean   = mean(ma),
    t           = unname(tt$statistic),
    df          = unname(tt$parameter),
    p           = tt$p.value,
    cohens_d    = d_ci["d"],
    d_ci_low    = d_ci["ci_low"],
    d_ci_high   = d_ci["ci_high"]
  )
}

sent_df <- map_dfr(platforms, function(plat) {
  map_dfr(affect_cols, function(col) run_affect_test(ghosts_known, plat, col))
}) %>%
  mutate(
    p_adj    = p.adjust(p, method = "bonferroni"),
    sig_adj  = p_to_stars(p_adj),
    reject_H0 = p_adj < 0.05
  )

sent_df
```

```{r results='asis'}
cat(
  sent_df %>%
    mutate(
      d_ci = paste0("[", round(d_ci_low, 3), ", ", round(d_ci_high, 3), "]"),
      across(where(is.numeric), ~round(., 4))
    ) %>%
    select(Platform, Metric, Female_n, Male_n,
           Female_mean, Male_mean, t, df, p, p_adj,
           cohens_d, d_ci, sig_adj) %>%
    kbl(format   = "latex",
        booktabs = TRUE,
        caption  = "Welch $t$-tests comparing female and male ghost affect scores across platforms (Bonferroni-adjusted).",
        col.names = c("Platform", "Metric", "$n_F$", "$n_M$",
                       "$\\bar{x}_F$", "$\\bar{x}_M$",
                       "$t$", "df", "$p$", "$p_{adj}$",
                       "Cohen's $d$", "95\\% CI", "Sig."),
        escape   = FALSE
    ) %>%
    kable_styling(latex_options = c("hold_position", "scale_down")) %>%
    footnote(
      general        = "Cohen's $d$ 95\\% CI computed via bootstrap (B = 2,000, seed = 42).",
      threeparttable = TRUE,
      escape         = FALSE
    )
)
```

### 7. Appeasement / euphemism chi-square

```{r}
# Reuse the already-loaded and standardized mentions_df (no need to re-read CSV).
appeasement_lexicon <- c(
  # Chinese
  "好兄弟", "不好意思", "請原諒", "對不起", "抱歉", "失禮", "無意冒犯",
  "保佑", "別見怪", "請息怒", "請高抬貴手", "拍謝", "超度", "金紙", "送走",
  "謝謝", "念佛", "超渡", "有應公", "萬善公", "感謝", "請走", "念經",

  # Korean
  "죄송", "미안", "용서", "화 풀", "실례", "괜찮으시면", "제발",
  "용서해", "화내지", "노하지", "살려주세요", "위령", "달래", "부탁",
  "감사", "무사히", "위로", "기도", "천도", "고사", "제물", "저승", "부디",
  "명복", "편히", "보살펴", "달래다", "49재", "천도재", "달래주다", "내세", "영계",

  # English
  "sorry", "forgive", "forgive me", "please don't", "please do not",
  "no offense", "i mean no harm", "spare me", "please", "pardon me",
  "leave me alone", "rest in peace", "bless", "appease", "offering", "pray",
  "protect", "go away", "pass away", "apologize", "thank you", "i respect",
  "i apologize", "peace be with", "spirit world", "afterlife", "respect",
  "condolences", "sympathize", "spirit realm"
)
```

```{r}
escape_regex <- function(x) {
  str_replace_all(x, "([.|()\\^{}+$*?]|\\[|\\]|\\\\)", "\\\\\\1")
}

appeasement_pattern <- appeasement_lexicon %>%
  escape_regex() %>%
  str_c(collapse = "|")

mentions_df <- mentions_df %>%
  mutate(
    has_appeasement = as.integer(
      str_detect(sentence, regex(appeasement_pattern, ignore_case = TRUE))
    ),
    has_appeasement = replace_na(has_appeasement, 0L)
  )
```

```{r}
run_appeasement_chisq <- function(data, platform_name) {
  sub <- data %>%
    filter(
      platform == platform_name,
      gender_new %in% c("Female", "Male"),
      !is.na(has_appeasement)
    )

  if (!all(c("Female", "Male") %in% unique(sub$gender_new))) return(NULL)

  ct <- table(sub$gender_new, sub$has_appeasement)
  if (nrow(ct) != 2 || ncol(ct) != 2) return(NULL)
  if (!("1" %in% colnames(ct)))       return(NULL)
  if (sum(ct[, "1"]) == 0)            return(NULL)

  test  <- chisq.test(ct, correct = TRUE)
  cv    <- effectsize::cramers_v(ct)
  expected_min <- min(test$expected)

  # Fisher fallback when expected counts are too small (cf. space_color)
  if (expected_min < 5) {
    fisher_res <- fisher.test(ct)
    tibble(
      platform    = platform_name,
      chi2        = NA_real_,
      df          = NA_real_,
      p_value     = fisher_res$p.value,
      cramers_v   = cv$Cramers_v[1],
      test_used   = "Fisher",
      expected_min = expected_min
    )
  } else {
    tibble(
      platform    = platform_name,
      chi2        = unname(test$statistic),
      df          = unname(test$parameter),
      p_value     = test$p.value,
      cramers_v   = cv$Cramers_v[1],
      test_used   = "Chi-square",
      expected_min = expected_min
    )
  }
}

appeasement_results <- map_dfr(
  c("ptt", "reddit", "theqoo"),
  ~run_appeasement_chisq(mentions_df, .x)
)

appeasement_results
```

```{r results='asis'}
cat(
  appeasement_results %>%
    mutate(
      sig = p_to_stars(p_value),
      across(where(is.numeric), ~round(., 4))
    ) %>%
    select(platform, test_used, chi2, df, p_value, cramers_v, sig) %>%
    kbl(format   = "latex",
        booktabs = TRUE,
        caption  = "Appeasement/euphemism rates by ghost gender (Fisher's exact test used when expected count $< 5$).",
        col.names = c("Platform", "Test", "$\\chi^2$", "df", "$p$", "Cram\\'{e}r's $V$", "Sig."),
        escape   = FALSE
    ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

### 8. Classification metrics + Cohen's kappa

Unknown is included as a full class in all evaluation metrics. Excluding Unknown would silently drop false positives where the system confidently predicts Female/Male on truly ambiguous examples, inflating reported performance. Cohen's κ already includes Unknown; P/R/F1, McNemar, and bootstrap CI now do the same for consistency.

```{r}
completed <- read_csv(
  "results/annotation_task_completed_with_methods.csv",
  show_col_types = FALSE
)
completed <- completed %>% rename_with(str_trim)

# All labels including Unknown — used for ALL evaluation metrics
valid_gender <- c("Female", "Male", "Unknown")
valid_state  <- c("Alive", "Deceased", "Supernatural", "Unknown")
```

#### 8.1 Helper

```{r}
get_classification_metrics_exact <- function(truth, pred, labels) {
  truth <- factor(truth, levels = labels)
  pred  <- factor(pred,  levels = labels)

  cm      <- confusionMatrix(pred, truth)
  byclass <- cm$byClass

  if (is.null(dim(byclass))) {
    tibble(
      class     = labels[1],
      precision = unname(byclass["Pos Pred Value"]),
      recall    = unname(byclass["Sensitivity"]),
      f1        = unname(byclass["F1"])
    )
  } else {
    tibble(
      class     = str_remove(rownames(byclass), "^Class:\\s*"),
      precision = byclass[, "Pos Pred Value"],
      recall    = byclass[, "Sensitivity"],
      f1        = byclass[, "F1"]
    )
  }
}
```

#### 8.2 Gender metrics

```{r}
g_df <- completed %>% filter(human_gender %in% valid_gender)

gender_rb_metrics <- get_classification_metrics_exact(
  truth  = g_df$human_gender,
  pred   = replace_na(g_df$rb_gender, "Unknown"),
  labels = valid_gender
) %>% mutate(model = "Rule-Based", task = "Gender")

gender_cs_metrics <- get_classification_metrics_exact(
  truth  = g_df$human_gender,
  pred   = replace_na(g_df$cascade_gender, "Unknown"),
  labels = valid_gender
) %>% mutate(model = "Cascade", task = "Gender")

gender_kappa <- tibble(
  task  = "Gender",
  model = c("Rule-Based", "Cascade"),
  kappa = c(
    irr::kappa2(data.frame(
      truth = factor(g_df$human_gender, levels = valid_gender),
      pred  = factor(replace_na(g_df$rb_gender, "Unknown"), levels = valid_gender)
    ))$value,
    irr::kappa2(data.frame(
      truth = factor(g_df$human_gender, levels = valid_gender),
      pred  = factor(replace_na(g_df$cascade_gender, "Unknown"), levels = valid_gender)
    ))$value
  )
)
```

#### 8.3 State metrics

```{r}
s_df <- completed %>% filter(human_state %in% valid_state)

state_rb_metrics <- get_classification_metrics_exact(
  truth  = s_df$human_state,
  pred   = replace_na(s_df$rb_state, "Unknown"),
  labels = valid_state
) %>% mutate(model = "Rule-Based", task = "State")

state_cs_metrics <- get_classification_metrics_exact(
  truth  = s_df$human_state,
  pred   = replace_na(s_df$cascade_state, "Unknown"),
  labels = valid_state
) %>% mutate(model = "Cascade", task = "State")

state_kappa <- tibble(
  task  = "State",
  model = c("Rule-Based", "Cascade"),
  kappa = c(
    irr::kappa2(data.frame(
      truth = factor(s_df$human_state, levels = valid_state),
      pred  = factor(replace_na(s_df$rb_state, "Unknown"), levels = valid_state)
    ))$value,
    irr::kappa2(data.frame(
      truth = factor(s_df$human_state, levels = valid_state),
      pred  = factor(replace_na(s_df$cascade_state, "Unknown"), levels = valid_state)
    ))$value
  )
)
```

#### 8.4 Macro-F1

```{r}
# Compute macro-F1 for every task × model using the sklearn-style helper
macro_f1_section8 <- tibble(
  task  = c("Gender", "Gender", "State", "State"),
  model = c("Rule-Based", "Cascade", "Rule-Based", "Cascade"),
  macro_f1 = c(
    macro_f1_sklearn_style(g_df$human_gender,
                           replace_na(g_df$rb_gender, "Unknown"),      valid_gender),
    macro_f1_sklearn_style(g_df$human_gender,
                           replace_na(g_df$cascade_gender, "Unknown"), valid_gender),
    macro_f1_sklearn_style(s_df$human_state,
                           replace_na(s_df$rb_state, "Unknown"),      valid_state),
    macro_f1_sklearn_style(s_df$human_state,
                           replace_na(s_df$cascade_state, "Unknown"), valid_state)
  )
)
```

#### 8.5 LaTeX — Per-class metrics

```{r results='asis'}
all_metrics <- bind_rows(
  gender_rb_metrics, gender_cs_metrics,
  state_rb_metrics,  state_cs_metrics
) %>%
  select(task, model, class, precision, recall, f1) %>%
  mutate(across(where(is.numeric), ~round(., 4)))

cat(
  kbl(all_metrics,
      format    = "latex",
      booktabs  = TRUE,
      caption   = "Per-class precision, recall, and F1 for gender and state classification (all labels including Unknown).",
      col.names = c("Task", "Model", "Class", "Precision", "Recall", "F1"),
      escape    = FALSE
  ) %>%
    kable_styling(latex_options = c("hold_position")) %>%
    collapse_rows(columns = 1:2, valign = "top", latex_hline = "major")
)
```

#### 8.6 LaTeX — Macro-F1 + Cohen's κ

```{r results='asis'}
all_kappa <- bind_rows(gender_kappa, state_kappa)

summary_section8 <- all_kappa %>%
  left_join(macro_f1_section8, by = c("task", "model")) %>%
  select(task, model, macro_f1, kappa) %>%
  mutate(across(where(is.numeric), ~round(., 4)))

cat(
  kbl(summary_section8,
      format    = "latex",
      booktabs  = TRUE,
      caption   = "Macro-F1 and Cohen's $\\kappa$ for gender and state classification (all labels including Unknown).",
      col.names = c("Task", "Model", "Macro-F1", "$\\kappa$"),
      escape    = FALSE
  ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

### 9. Exact McNemar + bootstrap 95% CI

#### 9.1 McNemar

```{r}
run_exact_mcnemar <- function(data, truth_col, rb_col, cs_col,
                              valid_labels, task_name) {
  df_t <- data %>% filter(.data[[truth_col]] %in% valid_labels)

  ytrue <- df_t[[truth_col]]
  yrb   <- replace_na(df_t[[rb_col]], "Unknown")
  ycs   <- replace_na(df_t[[cs_col]], "Unknown")

  rb_correct <- yrb == ytrue
  cs_correct <- ycs == ytrue

  b <- sum((!rb_correct) & cs_correct, na.rm = TRUE)
  c_val <- sum(rb_correct & (!cs_correct), na.rm = TRUE)

  discordant <- b + c_val

  if (discordant == 0) {
    p_val <- 1
  } else {
    p_val <- stats::binom.test(
      x           = min(b, c_val),
      n           = discordant,
      p           = 0.5,
      alternative = "two.sided"
    )$p.value
  }

  tibble(
    task    = task_name,
    b       = b,
    c       = c_val,
    p_value = p_val
  )
}

mcn_gender <- run_exact_mcnemar(
  completed,
  truth_col    = "human_gender",
  rb_col       = "rb_gender",
  cs_col       = "cascade_gender",
  valid_labels = valid_gender,
  task_name    = "Gender"
)

mcn_state <- run_exact_mcnemar(
  completed,
  truth_col    = "human_state",
  rb_col       = "rb_state",
  cs_col       = "cascade_state",
  valid_labels = valid_state,
  task_name    = "State"
)

bind_rows(mcn_gender, mcn_state)
```

#### 9.2 Bootstrap macro-F1 CI

```{r}
gender_boot <- completed %>%
  filter(human_gender %in% valid_gender) %>%
  mutate(
    rb_gender      = replace_na(rb_gender, "Unknown"),
    cascade_gender = replace_na(cascade_gender, "Unknown")
  )

gender_rb_ci <- bootstrap_macro_f1_exact(
  gender_boot,
  truth_col = "human_gender",
  pred_col  = "rb_gender",
  labels    = valid_gender
) %>% mutate(task = "Gender", model = "Rule-Based")

gender_cs_ci <- bootstrap_macro_f1_exact(
  gender_boot,
  truth_col = "human_gender",
  pred_col  = "cascade_gender",
  labels    = valid_gender
) %>% mutate(task = "Gender", model = "Cascade")

state_boot <- completed %>%
  filter(human_state %in% valid_state) %>%
  mutate(
    rb_state      = replace_na(rb_state, "Unknown"),
    cascade_state = replace_na(cascade_state, "Unknown")
  )

state_rb_ci <- bootstrap_macro_f1_exact(
  state_boot,
  truth_col = "human_state",
  pred_col  = "rb_state",
  labels    = valid_state
) %>% mutate(task = "State", model = "Rule-Based")

state_cs_ci <- bootstrap_macro_f1_exact(
  state_boot,
  truth_col = "human_state",
  pred_col  = "cascade_state",
  labels    = valid_state
) %>% mutate(task = "State", model = "Cascade")

boot_ci_all <- bind_rows(gender_rb_ci, gender_cs_ci, state_rb_ci, state_cs_ci)
boot_ci_all
```

#### 9.3 LaTeX

```{r results='asis'}
cat(
  bind_rows(mcn_gender, mcn_state) %>%
    mutate(
      sig = p_to_stars(p_value),
      across(where(is.numeric), ~round(., 4))
    ) %>%
    kbl(format    = "latex",
        booktabs  = TRUE,
        caption   = "Exact McNemar tests comparing rule-based and cascade systems.",
        col.names = c("Task", "$b$", "$c$", "$p$", "Sig."),
        escape    = FALSE
    ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

```{r results='asis'}
cat(
  boot_ci_all %>%
    select(task, model, estimate, ci_low, ci_high) %>%
    mutate(across(where(is.numeric), ~round(., 4))) %>%
    kbl(format    = "latex",
        booktabs  = TRUE,
        caption   = "Bootstrap 95\\% confidence intervals for macro-F1.",
        col.names = c("Task", "Model", "Macro-F1", "CI Low", "CI High"),
        escape    = FALSE
    ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

### 10. LLM-as-Judge supplementary metrics

```{r}
judge_df <- read_csv(
  "results/llm_as_judge_results.csv",
  show_col_types = FALSE
)

judge_gender <- judge_df %>%
  filter(gold_gender_sonnet %in% valid_gender) %>%
  mutate(
    gold_gender_sonnet = factor(replace_na(gold_gender_sonnet, "Unknown"), levels = valid_gender),
    gender_cascade     = factor(replace_na(gender_cascade, "Unknown"),     levels = valid_gender)
  )

judge_gender_metrics <- get_classification_metrics_exact(
  truth  = judge_gender$gold_gender_sonnet,
  pred   = judge_gender$gender_cascade,
  labels = valid_gender
) %>% mutate(task = "Gender", model = "Cascade vs Sonnet")

judge_state <- judge_df %>%
  filter(gold_state_sonnet %in% valid_state) %>%
  mutate(
    gold_state_sonnet = factor(replace_na(gold_state_sonnet, "Unknown"), levels = valid_state),
    state_cascade     = factor(replace_na(state_cascade, "Unknown"),     levels = valid_state)
  )

judge_state_metrics <- get_classification_metrics_exact(
  truth  = judge_state$gold_state_sonnet,
  pred   = judge_state$state_cascade,
  labels = valid_state
) %>% mutate(task = "State", model = "Cascade vs Sonnet")

judge_kappa <- tibble(
  task  = c("Gender", "State"),
  model = c("Cascade vs Sonnet", "Cascade vs Sonnet"),
  kappa = c(
    kappa2(data.frame(
      rater1 = as.character(judge_gender$gold_gender_sonnet),
      rater2 = as.character(judge_gender$gender_cascade)
    ))$value,
    kappa2(data.frame(
      rater1 = as.character(judge_state$gold_state_sonnet),
      rater2 = as.character(judge_state$state_cascade)
    ))$value
  )
)

# Macro-F1 point estimate
judge_macro_f1 <- tibble(
  task  = c("Gender", "State"),
  model = c("Cascade vs Sonnet", "Cascade vs Sonnet"),
  macro_f1 = c(
    macro_f1_sklearn_style(
      as.character(judge_gender$gold_gender_sonnet),
      as.character(judge_gender$gender_cascade),
      valid_gender),
    macro_f1_sklearn_style(
      as.character(judge_state$gold_state_sonnet),
      as.character(judge_state$state_cascade),
      valid_state)
  )
)

# Bootstrap 95% CI for macro-F1
judge_gender_df <- tibble(
  truth = as.character(judge_gender$gold_gender_sonnet),
  pred  = as.character(judge_gender$gender_cascade)
)
judge_state_df <- tibble(
  truth = as.character(judge_state$gold_state_sonnet),
  pred  = as.character(judge_state$state_cascade)
)

judge_gender_ci <- bootstrap_macro_f1_exact(
  judge_gender_df, "truth", "pred", valid_gender
) %>% mutate(task = "Gender", model = "Cascade vs Sonnet")

judge_state_ci <- bootstrap_macro_f1_exact(
  judge_state_df, "truth", "pred", valid_state
) %>% mutate(task = "State", model = "Cascade vs Sonnet")

judge_boot_ci <- bind_rows(judge_gender_ci, judge_state_ci)
```

```{r results='asis'}
judge_all_metrics <- bind_rows(judge_gender_metrics, judge_state_metrics) %>%
  select(task, model, class, precision, recall, f1) %>%
  mutate(across(where(is.numeric), ~round(., 4)))

cat(
  kbl(judge_all_metrics,
      format    = "latex",
      booktabs  = TRUE,
      caption   = "LLM-as-Judge: per-class metrics, cascade system vs.\\ Sonnet gold labels.",
      col.names = c("Task", "Model", "Class", "Precision", "Recall", "F1"),
      escape    = FALSE
  ) %>%
    kable_styling(latex_options = c("hold_position")) %>%
    collapse_rows(columns = 1:2, valign = "top", latex_hline = "major")
)
```

```{r results='asis'}
judge_summary <- judge_kappa %>%
  left_join(judge_macro_f1, by = c("task", "model")) %>%
  left_join(
    judge_boot_ci %>% select(task, model, ci_low, ci_high),
    by = c("task", "model")
  ) %>%
  select(task, model, macro_f1, ci_low, ci_high, kappa) %>%
  mutate(across(where(is.numeric), ~round(., 4)))

cat(
  kbl(judge_summary,
      format    = "latex",
      booktabs  = TRUE,
      caption   = "LLM-as-Judge summary: macro-F1 (with bootstrap 95\\% CI) and Cohen's $\\kappa$.",
      col.names = c("Task", "Model", "Macro-F1", "CI Low", "CI High", "$\\kappa$"),
      escape    = FALSE
  ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

### 11. Per-category article-level Fisher / Chi-square tests (Space · Color · Haunting Method)

Replicates the article-level statistical tests from the `space_color_haunted_method` notebook: for each category within each platform, builds a 2×2 contingency table (Female hits / no-hit vs Male hits / no-hit) and applies chi-square with Fisher's exact test fallback when any expected cell count \< 5.

#### 11.1 Keyword dictionaries

```{r}
# ── SPACE ─────────────────────────────────────────────────────────────────────
space_groups <- list(
  ptt = list(
    `Indoor (Domestic)` = c('房間', '房門','廚房','臥房','阿太房','空房','病房',
                    '客房','房屋','暗房','樓房','新房子','雅房','大房子','書房',
                    '小房','平房','套房','茅房','小書房','睡房','老房子','房子','大樓',
                    '閣樓','儲藏室','和室','休息室','山莊',
                    '紅眠床','大床','病床','彈簧床','床位','床沿','床邊'),
    Sleep_Dream = c('常夢','夢見','鄰居托夢','時托夢','夢境','入夢','夢到那','夢到','噩夢',
      '惡夢','實夢','夢中聞','夢鄉','夢話','夢樂透','做夢','作夢','托夢','夢醒',
      '夢過','姊托夢','夢遊','夢魘','睡著','睡醒','睡覺','午睡','睡到',
      '晚睡','熟睡','睡眠','昏睡','睡意','半睡半醒','睡死','打瞌睡','入睡'),
    Bathroom   = c('廁所'),
    Window     = c('窗戶','窗簾','落地窗','氣窗','紙窗','窗台','玻璃窗','門窗','車窗',
      '紗窗','小窗','外窗','櫥窗','鐵窗'),
    Hallway    = c('走廊','黑長廊','長廊'),
    Stairs     = c('樓梯角','樓梯口','樓梯'),
    School     = c('學校','教室','宿舍','女生宿舍','男生宿舍','校園','夜校','校舍','住校',
      '研究室','實驗室','大學','小學','中學','宿營','研究所'),
    Outdoor    = c('金寶山','柏油路','車站','岔路','公路','小路','巡山','騎樓','佛光山','登山','金山',
      '高山','山徑','武山','濱海','霞海','南海','海灘','斑馬線','黑森林','教會','墓地',
      '墳墓區','墳墓','墓園','捷運站','車道','車場','公園','廟口','妻廟','祖師廟',
      '桃園大廟','古廟','公廟','廟寺','大廟'),
    `Military Setting` = c('部隊','查房','巡房','軍械室','國軍','軍區','軍卡車',
                     '美軍','軍方','軍隊','軍艦','軍機','軍工','行軍','軍校','軍旅','海軍',
                     '日軍','軍徽','單位','兵部','指揮部','旅部','營部',
                     '全營','營舍','營區','摸哨','哨站','站哨','撤哨','哨屋',
                     '接哨','上哨','下哨','外哨','哨點','哨所','內務櫃','戰車','甲車','碉堡')
  ),
  theqoo = list(
    `Indoor (Domestic)` = c('안방','침대','주방','방바닥','거실','독실','창고','숙소'),
    Sleep_Dream = c('꿈꾸','꿈속','잠들','잠결','잠자','낮잠'),
    Bathroom    = c('화장실'),
    Window      = c('창문','창가','창호지'),
    Hallway     = c('복도','현관'),
    Stairs      = c('계단'),
    School      = c('고등학교','교실','강의실','학교','초등학교','기숙사','대학'),
    Outdoor     = c('숲','무덤','강원도','횡단보도','산길','사거리','뒷산',
      '첩첩산중','교회','지하철','공원'),
    `Military Setting` = c('중대','대대장','부대','초소','행보관')
  ),
  reddit = list(
    `Indoor (Domestic)` = c('room', 'bedroom', 'kitchen','house','playroom','storeroom',
                    'living room','livingroom','sunroom','guesthouse',
                    'warehouse','haunted house','townhouse','farmhouse','coachhouse',
                    'abandoned house','bedside'),
    Sleep_Dream = c('dream','sleep paralysis','asleep','dreamed','dreaming','half-asleep',
      'sleeper','sleepwalking','sleeping','half asleep','sleep','sleepwalk'),
    Bathroom    = c('bathroom','restroom','washroom','toilet'),
    Window      = c('window','windowsill'),
    Hallway     = c('hallway','corridor','hall','aisle','passage'),
    Stairs      = c('stair','stairwell','staircase','downstairs','upstairs','downstair','stairs'),
    School      = c('abandoned school','highschool','school','preschool',
      'classroom','dormitory','dorm','elementary'),
    Outdoor     = c('church','ballroom','shophouse','lighthouse','dirtroad','roadside','backroad',
      'railroad','crossroad','road','forest','woodland','woode','greenwood',
      'graveyard','gravesite','cemetery','park','temple','subway','sidewalk'),
    `Military Setting` = c('military','army','military base','soldier','navy')
  )
)

# ── COLOR ─────────────────────────────────────────────────────────────────────
color_groups <- list(
  ptt = list(
    White  = c('白衣','白色','全白','襲白','穿白','褲白鞋','白鞋','白點','白袍','白光','白線','青白','發白','白面','白霧','白布','白影'),
    Red    = c('紅紙','紅裙','紅影','紅點','紅絲','染紅','紅字畫','紅布','紅褲','發紅','紅線','紅光','血色'),
    Black  = c('黑影','黑鬼','黑氣','黑色','黑青','烏黑','黑衣服','黑服','全黑','焦黑','黑衣','黑人','發黑','灰黑色','黑霧','黑煙','暗黑','黑面','黑衣人'),
    Green  = c('綠氣','綠霧','綠衣','綠光','綠綠','陣綠光','草綠服','變綠','青色'),
    Blue   = c('藍光','藍面','藏青色','鬼火'),
    Yellow = c('黃衣','黃光'),
    Pink   = c('粉色'),
    Brown  = c('褐色','咖啡色'),
    Grey   = c('灰色','灰白色'),
    Orange = c('橘色','金色'),
    Purple = c('紫衣')
  ),
  theqoo = list(
    White  = c('창백','소복','흰색','하얀색','백발'),
    Red    = c('빨간색','피눈물'),
    Black  = c('흑색','그림자'),
    Blue   = c('파란색','도깨비불','파랑색'),
    Green  = c('초록'),
    Brown  = c('갈색'),
    Pink   = c('핑크색'),
    Grey   = c('회백색','회색'),
    Purple = c('연보라색')
  ),
  reddit = list(
    White  = c('pale','whiteish','white','colorless'),
    Red    = c('redheade','reddish','red','bloody','bloodstained','bloodied','blood'),
    Pink   = c('pink'),
    Black  = c('darken','dark','darkest','darker','darkness','blacken','blacker','blackness','black','pitch','shadow person','shadow figure','shadows','shadow','shadowy','shadowed'),
    Grey   = c('grey','gray','greyish','grayish'),
    Green  = c('green','greenish'),
    Blue   = c('blue','blueish'),
    Purple = c('purple'),
    Brown  = c('brown','brownish')
  )
)

# ── HAUNTING METHOD ───────────────────────────────────────────────────────────
haunting_method_groups <- list(
  ptt = list(
    Sound = c('敲打','尖叫','嚎啕大哭','哭泣','叫喚','叫出','狂叫','大叫','大吼大叫',
      '吠叫','喊叫','哀叫','哭叫','叫住','叫著','嚎叫','呼叫','叫喊','怪叫','吼叫',
      '狗叫','叫醒','敲門','敲著','敲敲','敲擊','鬼哭','痛哭','哭醒','哭喊','大哭',
      '爆哭','嘶吼','吼聲','狂吼','怒吼','斯吼','人聲','女聲','低聲','小聲','作聲','輕聲',
      '大聲','門聲','鍵盤聲','聲音','聲調','高聲','出聲','聲響','彈珠聲','氣聲','鬼聲','鈴聲',
      '男聲','雜聲','鈴鐺聲','銅鈴聲','翁翁聲','回音','童音','噪音','雜音','氣音','吹口哨','風聲',
      '唱歌','歌聲','獰笑','發笑','咧嘴一笑','嘻笑','笑容','笑笑','笑著','狂笑','微笑',
      '奸笑','大笑','冷笑'),
    Touch = c('抓著','抓出去','抓走','抓痕','抓住','抓到','拉著','拉下去','拉腳','往下拉','猛拍',
      '拍肩膀','拍打','觸碰','碰觸','碰到','觸摸','撫摸','手摸','摸到','摸摸','摸著','山風','海風',
      '冷風','狂風','大風','微風','寒風','涼風','推開','推下去','推著','推下'),
    Visual_Appearance = c('注視','出現','站著','站立','看見','盯著','盯上','對視'),
    Movement = c('消失','進房','靠窗','跟到','跟來','跟去','跟壓','壓床','壓著',
      '上樓','下樓','墜樓','跳樓','上頂樓','跳海','落海','打開',
      '壓制','鬼壓','壓到','被壓','壓住','人壓','壓過','擠壓',
      '飄出','飄去','飄移','飄起','飄過','飄走','飄動','飄浮','飄著',
      '飄進','穿越','穿門','穿梭','狂奔','奔跑','跑步','跑掉','飛奔',
      '附著','依附','附身')
  ),
  theqoo = list(
    Sound = c('휘파람','물소리','노랫소리','소리','목소리','발소리','소리치',
      '울컥','울리','울음','외치','웃음'),
    Touch = c('손길','바람','붙잡히','잡히','만지','어루만지','만지작','끌어안','끌려가','밀어내'),
    Visual_Appearance = c('바라보','돌아보','노려보','지켜보','내려다보','쳐다보','보이다',
      '나타나','다가서','뒤돌아서'),
    Movement = c('가위눌리','가위눌림','가위','따라오','누르','따라가','지나가','지나','지나치','사라지',
      '움직이','뛰쳐나오','뛰어오','뛰어나가','씌이','빙의')
  ),
  reddit = list(
    Sound = c('scream','screaming','voice','disembodied voice','disembodied','shrieking',
      'shriek','crying','cry','breath','breathing','breathe','laughing','laugher',
      'laughter','laugh','whistle','sound','sounding','shout','shouting','shouted'),
    Touch = c('pull','tapping','tap','grab','touch','touching','push','slam','pushing','slamming'),
    Visual_Appearance = c('watching','reappear','appear','standing','stare','watch','see','unseen','saw'),
    Movement = c('move','disappear','disappearing','dissappeare','disappearance','following','follow',
      'walking','walk','vanish','vanishing','float','floated','running','run',
      'possessed','possess','possession')
  )
)
```

#### 11.2 Core function: article-level presence + Fisher / Chi-square

```{r}
# Map platform → language for regex boundary logic
platform_lang <- c(ptt = "zh", theqoo = "ko", reddit = "en")

build_keyword_pattern <- function(keywords, lang) {
  # Sort by length descending (longer keywords first, avoids partial matches)
  kws <- unique(trimws(keywords))
  kws <- kws[order(nchar(kws), decreasing = TRUE)]

  if (lang == "en") {
    # Word-boundary matching for English
    parts <- paste0("(?<!\\w)", str_replace_all(kws, "([\\.\\|\\(\\)\\^\\{\\}\\+\\$\\*\\?\\[\\]\\\\])", "\\\\\\1"), "(?!\\w)")
    regex(paste(parts, collapse = "|"), ignore_case = TRUE)
  } else {
    # Plain string matching for CJK (Chinese / Korean)
    parts <- str_replace_all(kws, "([\\.\\|\\(\\)\\^\\{\\}\\+\\$\\*\\?\\[\\]\\\\])", "\\\\\\1")
    regex(paste(parts, collapse = "|"))
  }
}

run_category_article_tests <- function(ghosts_df, groups_dict, plat_name) {
  lang <- platform_lang[[plat_name]]

  plat_ghosts <- ghosts_df %>%
    filter(tolower(trimws(platform)) == tolower(plat_name))

  if (nrow(plat_ghosts) == 0) return(NULL)

  # Use context if available, otherwise sentence
  if ("context" %in% names(plat_ghosts)) {
    plat_ghosts <- plat_ghosts %>%
      mutate(scan_text = if_else(!is.na(context) & trimws(context) != "",
                                 context, sentence))
  } else {
    plat_ghosts <- plat_ghosts %>% mutate(scan_text = sentence)
  }

  # Base article counts per gender (unique article_id × gender_new)
  base_articles <- plat_ghosts %>%
    distinct(article_id, gender_new) %>%
    count(gender_new, name = "base_n") %>%
    deframe()

  map_dfr(names(groups_dict), function(cat_name) {
    kws     <- groups_dict[[cat_name]]
    pattern <- build_keyword_pattern(kws, lang)

    # Flag rows that match, then get unique (article_id, gender_new) hits
    hits <- plat_ghosts %>%
      filter(str_detect(scan_text, pattern)) %>%
      distinct(article_id, gender_new)

    hit_counts <- hits %>% count(gender_new, name = "hits") %>% deframe()

    f_hits <- unname(hit_counts["Female"]); if (is.na(f_hits)) f_hits <- 0L
    m_hits <- unname(hit_counts["Male"]);   if (is.na(m_hits)) m_hits <- 0L
    f_base <- unname(base_articles["Female"]); if (is.na(f_base)) f_base <- 0L
    m_base <- unname(base_articles["Male"]);   if (is.na(m_base)) m_base <- 0L

    f_nohit <- f_base - f_hits
    m_nohit <- m_base - m_hits

    # Skip if no hits at all
    if (f_hits + m_hits == 0) return(NULL)

    ct <- matrix(c(f_hits, m_hits, f_nohit, m_nohit), nrow = 2,
                 dimnames = list(c("Female", "Male"), c("Hit", "NoHit")))

    # Chi-square first; Fisher fallback if expected < 5
    chisq_res   <- tryCatch(chisq.test(ct, correct = TRUE), error = function(e) NULL)
    expected_min <- if (!is.null(chisq_res)) min(chisq_res$expected) else 0

    if (is.null(chisq_res) || expected_min < 5) {
      fisher_res <- fisher.test(ct)
      tibble(
        Platform     = plat_name,
        Category     = cat_name,
        Female_Hits  = f_hits, Female_Base = f_base,
        Male_Hits    = m_hits, Male_Base   = m_base,
        Female_Pct   = round(f_hits / max(f_base, 1) * 100, 2),
        Male_Pct     = round(m_hits / max(m_base, 1) * 100, 2),
        Test_Used    = "Fisher",
        Chi2         = NA_real_,
        df           = NA_real_,
        Expected_Min = expected_min,
        Odds_Ratio   = fisher_res$estimate,
        p_value      = fisher_res$p.value
      )
    } else {
      tibble(
        Platform     = plat_name,
        Category     = cat_name,
        Female_Hits  = f_hits, Female_Base = f_base,
        Male_Hits    = m_hits, Male_Base   = m_base,
        Female_Pct   = round(f_hits / max(f_base, 1) * 100, 2),
        Male_Pct     = round(m_hits / max(m_base, 1) * 100, 2),
        Test_Used    = "Chi-square",
        Chi2         = unname(chisq_res$statistic),
        df           = unname(chisq_res$parameter),
        Expected_Min = expected_min,
        Odds_Ratio   = (f_hits * m_nohit) / max(m_hits * f_nohit, 1),
        p_value      = chisq_res$p.value
      )
    }
  })
}
```

#### 11.3 Run tests for all three domains

```{r}
ghosts_for_cat <- mentions_df %>%
  filter(state_new == "Supernatural",
         gender_new %in% c("Female", "Male"),
         !is.na(platform))

# Space
space_stats <- map_dfr(c("ptt", "theqoo", "reddit"), function(p) {
  run_category_article_tests(ghosts_for_cat, space_groups[[p]], p)
}) %>% mutate(Domain = "Space")

# Color
color_stats <- map_dfr(c("ptt", "theqoo", "reddit"), function(p) {
  run_category_article_tests(ghosts_for_cat, color_groups[[p]], p)
}) %>% mutate(Domain = "Color")

# Haunting Method
method_stats <- map_dfr(c("ptt", "theqoo", "reddit"), function(p) {
  run_category_article_tests(ghosts_for_cat, haunting_method_groups[[p]], p)
}) %>% mutate(Domain = "Haunting Method")

cat_stats_all <- bind_rows(space_stats, color_stats, method_stats) %>%
  mutate(
    sig = p_to_stars(p_value)
  )

cat_stats_all
```

#### 11.4 LaTeX — Space

```{r results='asis'}
if (nrow(space_stats) > 0) {
  cat(
    space_stats %>%
      mutate(sig = p_to_stars(p_value),
             across(where(is.numeric), ~round(., 4))) %>%
      select(Platform, Category, Female_Hits, Female_Base, Female_Pct,
             Male_Hits, Male_Base, Male_Pct,
             Test_Used, Chi2, p_value, Odds_Ratio, sig) %>%
      kbl(format   = "latex",
          booktabs = TRUE,
          caption  = "Article-level gender distribution by space category (Fisher's exact test when expected $< 5$).",
          col.names = c("Platform", "Category",
                        "$n_F$", "Base$_F$", "\\%$_F$",
                        "$n_M$", "Base$_M$", "\\%$_M$",
                        "Test", "$\\chi^2$", "$p$", "OR", "Sig."),
          escape   = FALSE
      ) %>%
      kable_styling(latex_options = c("hold_position", "scale_down")) %>%
      collapse_rows(columns = 1, valign = "top", latex_hline = "major")
  )
}
```

#### 11.5 LaTeX — Color

```{r results='asis'}
if (nrow(color_stats) > 0) {
  cat(
    color_stats %>%
      mutate(sig = p_to_stars(p_value),
             across(where(is.numeric), ~round(., 4))) %>%
      select(Platform, Category, Female_Hits, Female_Base, Female_Pct,
             Male_Hits, Male_Base, Male_Pct,
             Test_Used, Chi2, p_value, Odds_Ratio, sig) %>%
      kbl(format   = "latex",
          booktabs = TRUE,
          caption  = "Article-level gender distribution by color category (Fisher's exact test when expected $< 5$).",
          col.names = c("Platform", "Category",
                        "$n_F$", "Base$_F$", "\\%$_F$",
                        "$n_M$", "Base$_M$", "\\%$_M$",
                        "Test", "$\\chi^2$", "$p$", "OR", "Sig."),
          escape   = FALSE
      ) %>%
      kable_styling(latex_options = c("hold_position", "scale_down")) %>%
      collapse_rows(columns = 1, valign = "top", latex_hline = "major")
  )
}
```

#### 11.6 LaTeX — Haunting Method

```{r results='asis'}
if (nrow(method_stats) > 0) {
  cat(
    method_stats %>%
      mutate(sig = p_to_stars(p_value),
             across(where(is.numeric), ~round(., 4))) %>%
      select(Platform, Category, Female_Hits, Female_Base, Female_Pct,
             Male_Hits, Male_Base, Male_Pct,
             Test_Used, Chi2, p_value, Odds_Ratio, sig) %>%
      kbl(format   = "latex",
          booktabs = TRUE,
          caption  = "Article-level gender distribution by haunting method (Fisher's exact test when expected $< 5$).",
          col.names = c("Platform", "Category",
                        "$n_F$", "Base$_F$", "\\%$_F$",
                        "$n_M$", "Base$_M$", "\\%$_M$",
                        "Test", "$\\chi^2$", "$p$", "OR", "Sig."),
          escape   = FALSE
      ) %>%
      kable_styling(latex_options = c("hold_position", "scale_down")) %>%
      collapse_rows(columns = 1, valign = "top", latex_hline = "major")
  )
}
```

### 12. Word2Vec cosine similarity: Kruskal-Wallis + pairwise Wilcoxon

Cosine similarity is bounded $[-1, 1]$ and typically non-normal, so we use non-parametric tests:

-   **Kruskal-Wallis** $H$ (non-parametric one-way ANOVA) to compare cosine similarity across groups
-   **Pairwise Wilcoxon rank-sum** (= Mann-Whitney $U$) with BH-FDR correction as post-hoc
-   **Rank-biserial correlation** $r$ as effect size

#### 12.1 Read Word2Vec results

```{r}
w2v_all <- read_csv(
  "results/w2v_thematic_all_platforms.csv",
  show_col_types = FALSE
)

# Keep only valid cosine similarity rows
w2v_valid <- w2v_all %>%
  filter(neighbour != "[NOT IN VOCAB]", !is.na(cosine_sim))

nrow(w2v_valid)
```

#### 12.2 Kruskal-Wallis: domains within each platform

```{r}
kw_by_platform <- w2v_valid %>%
  group_by(platform) %>%
  group_modify(~ {
    groups <- split(.x$cosine_sim, .x$domain)
    groups <- groups[sapply(groups, length) > 0]
    if (length(groups) < 2) return(tibble())
    kw <- kruskal.test(cosine_sim ~ domain, data = .x)
    tibble(
      H        = unname(kw$statistic),
      df       = unname(kw$parameter),
      p_value  = kw$p.value,
      n_groups = length(groups),
      total_n  = sum(sapply(groups, length))
    )
  }) %>%
  ungroup() %>%
  mutate(sig = p_to_stars(p_value))

kw_by_platform
```

#### 12.3 Pairwise Wilcoxon: domains within each platform (BH-FDR)

```{r}
pw_domain_rows <- list()
for (plat in unique(w2v_valid$platform)) {
  pdata <- w2v_valid %>% filter(platform == plat)
  domains <- sort(unique(pdata$domain))
  if (length(domains) < 2) next

  pairs <- combn(domains, 2, simplify = FALSE)
  for (pair in pairs) {
    g1 <- pdata %>% filter(domain == pair[1]) %>% pull(cosine_sim)
    g2 <- pdata %>% filter(domain == pair[2]) %>% pull(cosine_sim)
    if (length(g1) < 2 || length(g2) < 2) next

    wt <- wilcox.test(g1, g2, exact = FALSE)
    u  <- unname(wt$statistic)
    r_rb <- 1 - (2 * u) / (length(g1) * length(g2))

    pw_domain_rows[[length(pw_domain_rows) + 1]] <- tibble(
      platform = plat,
      group_1  = pair[1],
      group_2  = pair[2],
      n1       = length(g1),
      n2       = length(g2),
      U        = u,
      p_value  = wt$p.value,
      r_rb     = round(r_rb, 4)
    )
  }
}

pw_domain_df <- bind_rows(pw_domain_rows) %>%
  mutate(
    p_adj = p.adjust(p_value, method = "BH"),
    sig   = p_to_stars(p_adj)
  )

pw_domain_df
```

#### 12.4 Kruskal-Wallis: platforms within each domain

```{r}
kw_by_domain <- w2v_valid %>%
  group_by(domain) %>%
  group_modify(~ {
    groups <- split(.x$cosine_sim, .x$platform)
    groups <- groups[sapply(groups, length) > 0]
    if (length(groups) < 2) return(tibble())
    kw <- kruskal.test(cosine_sim ~ platform, data = .x)
    tibble(
      H        = unname(kw$statistic),
      df       = unname(kw$parameter),
      p_value  = kw$p.value,
      n_groups = length(groups),
      total_n  = sum(sapply(groups, length))
    )
  }) %>%
  ungroup() %>%
  mutate(sig = p_to_stars(p_value))

kw_by_domain
```

#### 12.5 Pairwise Wilcoxon: platforms within each domain (BH-FDR)

```{r}
pw_plat_rows <- list()
for (dom in unique(w2v_valid$domain)) {
  ddata <- w2v_valid %>% filter(domain == dom)
  plats <- sort(unique(ddata$platform))
  if (length(plats) < 2) next

  pairs <- combn(plats, 2, simplify = FALSE)
  for (pair in pairs) {
    g1 <- ddata %>% filter(platform == pair[1]) %>% pull(cosine_sim)
    g2 <- ddata %>% filter(platform == pair[2]) %>% pull(cosine_sim)
    if (length(g1) < 2 || length(g2) < 2) next

    wt <- wilcox.test(g1, g2, exact = FALSE)
    u  <- unname(wt$statistic)
    r_rb <- 1 - (2 * u) / (length(g1) * length(g2))

    pw_plat_rows[[length(pw_plat_rows) + 1]] <- tibble(
      domain     = dom,
      platform_1 = pair[1],
      platform_2 = pair[2],
      n1         = length(g1),
      n2         = length(g2),
      U          = u,
      p_value    = wt$p.value,
      r_rb       = round(r_rb, 4)
    )
  }
}

pw_plat_df <- bind_rows(pw_plat_rows) %>%
  mutate(
    p_adj = p.adjust(p_value, method = "BH"),
    sig   = p_to_stars(p_adj)
  )

pw_plat_df
```

#### 12.6 LaTeX — Kruskal-Wallis (domains within platform)

```{r results='asis'}
cat(
  kw_by_platform %>%
    mutate(across(where(is.numeric), ~round(., 4))) %>%
    kbl(format   = "latex",
        booktabs = TRUE,
        caption  = "Kruskal-Wallis $H$ tests: cosine similarity across thematic domains within each platform.",
        col.names = c("Platform", "$H$", "df", "$p$", "$k$", "$N$", "Sig."),
        escape   = FALSE
    ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

#### 12.7 LaTeX — Pairwise Wilcoxon (domains within platform)

```{r results='asis'}
if (nrow(pw_domain_df) > 0) {
  cat(
    pw_domain_df %>%
      mutate(across(where(is.numeric), ~round(., 4))) %>%
      select(platform, group_1, group_2, n1, n2, U, p_value, p_adj, r_rb, sig) %>%
      kbl(format   = "latex",
          booktabs = TRUE,
          caption  = "Pairwise Wilcoxon rank-sum tests (BH-FDR): cosine similarity between domains within each platform.",
          col.names = c("Platform", "Domain 1", "Domain 2",
                        "$n_1$", "$n_2$", "$U$",
                        "$p$", "$p_{adj}$", "$r_{rb}$", "Sig."),
          escape   = FALSE
      ) %>%
      kable_styling(latex_options = c("hold_position", "scale_down")) %>%
      collapse_rows(columns = 1, valign = "top", latex_hline = "major")
  )
}
```

#### 12.8 LaTeX — Kruskal-Wallis (platforms within domain)

```{r results='asis'}
cat(
  kw_by_domain %>%
    mutate(across(where(is.numeric), ~round(., 4))) %>%
    kbl(format   = "latex",
        booktabs = TRUE,
        caption  = "Kruskal-Wallis $H$ tests: cosine similarity across platforms within each thematic domain.",
        col.names = c("Domain", "$H$", "df", "$p$", "$k$", "$N$", "Sig."),
        escape   = FALSE
    ) %>%
    kable_styling(latex_options = c("hold_position"))
)
```

#### 12.9 LaTeX — Pairwise Wilcoxon (platforms within domain)

```{r results='asis'}
if (nrow(pw_plat_df) > 0) {
  cat(
    pw_plat_df %>%
      mutate(across(where(is.numeric), ~round(., 4))) %>%
      select(domain, platform_1, platform_2, n1, n2, U, p_value, p_adj, r_rb, sig) %>%
      kbl(format   = "latex",
          booktabs = TRUE,
          caption  = "Pairwise Wilcoxon rank-sum tests (BH-FDR): cosine similarity between platforms within each domain.",
          col.names = c("Domain", "Platform 1", "Platform 2",
                        "$n_1$", "$n_2$", "$U$",
                        "$p$", "$p_{adj}$", "$r_{rb}$", "Sig."),
          escape   = FALSE
      ) %>%
      kable_styling(latex_options = c("hold_position", "scale_down")) %>%
      collapse_rows(columns = 1, valign = "top", latex_hline = "major")
  )
}
```
